Model checking for simplified Naomi

### 2023-02-10 src/naomi-simple_model-checks/model-checks.Rmd
Trying to move forward to coverage assessment

>>>>

Discussion talking to Rachel:

* Can use samples from `tmb$fit$sample`
* Issue about one survey or two. Inclusion of two for the Malawi demo is more of a special case

Have the following samples from `rho_t1_out`:

```{r}
str(tmb$fit$sample$rho_t1_out)
```

Want to somehow line these up with the data from `tmb$outputs$inputs_outputs` or `tmb$outputs$indicators`.
Should be looking for some kind of `mf_out` object:

```{r}
str(tmb$outputs$fit)
```
